\LARGE \bf Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty

### 2014-12-30 paper.tex
Added pose equations and reference

The pose of an object $T$ is a member of the Lie Algebra $SO(3)$ in 3-dimensional space (something analogous holds for 2D).
This matrix is defined by 3 rotation angles $\bw = (\alpha, \beta, \gamma)$ and 3 translation coordinates $\bt = (t_x, t_y, t_z)$, summarized in parameter vector $\xi = (\bw, \bt)$.
One challenge with pose is that uncertainty in the pose matrix $T$ used to apply transformations is needed in practice, but uncertainty is mathematically more easily to quantify in terms of the pose parameters $\xi$.
Thus, to sample a pose matrix $T$ one can sample from a distribution on $\xi$ and compute the poes as:

>>>>

The pose of an object $T$ is a member of the Lie Algebra $SE(3)$ in 3-dimensional space (something analogous holds for 2D).
This matrix is defined by 3 rotation angles $\bw = (\alpha, \beta, \gamma)$ and 3 translation coordinates $\bt = (t_x, t_y, t_z)$, summarized in parameter vector $\mathbf{\xi} = (\bw, \bt)^T \in \mathbb{R}^6$.
One challenge with pose is that uncertainty in the pose matrix $T$ used to apply transformations is needed in practice, but uncertainty is mathematically more easily to quantify in terms of the pose parameters $\xi$.
Thus given a mean pose matrix $\bar{T} \in SE(3)$ and zero-mean uncertainty on the pose parameters $\mathbf{\xi} \sim \mN \left( \mathbf{0}, \Sigma \right)$ we define the pose random variable $T$ as

\vspace{-2ex}
\begin{align*}
	T  &= \exp \left( \mathbf{\xi}^{\wedge} \right) \bar{T}
\end{align*}

\noindent where the $\wedge$ operator is defined as in \cite{barfoot2014Pose}.
